Analyse from review

### 2021-05-17 manuscript/bef_stability/review_analysis.Rmd
Add BOD to SEM figures + change correlation in review

```{r}
library(ncdf4)
library(raster)
library(sf)
cru_file <- list.files(mypath("data-raw", "cru"))[!str_detect(list.files(mypath("data-raw", "cru")), "gz")]
nc.pre <- nc_open(mypath("data-raw", "cru", "cru_ts4.03.2011.2018.tmp.dat.nc"))

l <- map(cru_file, function (x) {
  pre <- raster::brick(mypath("data-raw", "cru", x), varname="tmp")
  extract(pre, st_wgs)
		 }
)

tmean <- do.call(cbind, l)
rownames(tmean) <- st_wgs$station
colnames(tmean) <- paste0(rep(c(paste0(0, seq(1,9)), seq(10, 12)), 2018 - 1991), "_", rep(seq(1991, 2018), each = 12))

# Correlation mean air temperature / water temperature
air_mean_temp <-
  rowMeans(tmean[, which(colnames(tmean) == "01_1995"):which(colnames(tmean) == "12_2018")]) 
air_temp <- enframe(air_mean_temp, name = "station", value = "air_95_18") %>%
  mutate(
    station = as.integer(station),
    air_06_18 = rowMeans(
      tmean[, which(colnames(tmean) == "01_2006"):which(colnames(tmean) == "12_2018")]
    )
  )

myload(habitat_press, sem_data, dir = mypath("data"))
temp_avg_comp <- habitat_press %>%
  dplyr::select(station, temperature_med) %>%
  left_join(air_temp, by = "station") %>%
  rename(water_06_2018 = temperature_med) %>%
  filter(station %in% sem_data$station)

dev.new(width = 6, height = 6, units = "cm")
# i3: mod + shift + space 
png(
  file = mypath("manuscript", "bef_stability", "figs",
    "pairs_temperature_plot.png")
)
pairs(
  temp_avg_comp[, 2:4], pch = 19 
)
dev.off()

mat <- round(cor(temp_avg_comp[, 2:4]), 3)
write.table(mat,
  file = mypath("manuscript", "bef_stability", "result", "cor_mat_temp.txt"),
  sep = ",",
  quote = FALSE,
  row.names = T)

# Test with monthly data
myload(yearly_temp_press_interp_mv_avg, dir = mypath("data-raw", "temp"))
temp <- yearly_temp_press_interp_mv_avg %>%
  group_by(id, year) %>%
  arrange(value.predSE) %>%
  slice(1) %>%
  select(station = id, year, temp = value_corrected) %>%
  mutate(temp = ifelse(temp > 45, NA, temp)) %>%
  ungroup()

#plot(pre[[1]])
#
#uk.area <- extent(-12, 4, 48, 64)
#uk <- crop(pre, uk.area)
#plot(uk)
#st <- get_basin_station(sf =TRUE)
#st_wgs <- st_transform(st, crs = 4326)
#
#test <- extract(pre, st_wgs)
```

>>>>

```{r}
library(ncdf4)
library(raster)
library(sf)
myload(habitat_press, sem_data, dir = mypath("data"))
st_wgs <- station_analysis %>%
  filter(id %in% sem_data$station)

cru_file <- list.files(mypath("data-raw", "cru"))[!str_detect(list.files(mypath("data-raw", "cru")), "gz")]
nc.pre <- nc_open(mypath("data-raw", "cru", "cru_ts4.03.2011.2018.tmp.dat.nc"))

l <- map(cru_file, function (x) {
  pre <- raster::brick(mypath("data-raw", "cru", x), varname="tmp")
  extract(pre, st_wgs)
		 })

tmean <- do.call(cbind, l)
rownames(tmean) <- st_wgs$id
colnames(tmean) <- paste0(rep(c(paste0(0, seq(1,9)), seq(10, 12)), 2018 - 1991), "_", rep(seq(1991, 2018), each = 12))

# Correlation mean air temperature / water temperature
air_mean_temp <-
  rowMeans(tmean[, which(colnames(tmean) == "01_1995"):which(colnames(tmean) == "12_2018")]) 
air_temp <- enframe(air_mean_temp, name = "station", value = "air_95_18") %>%
  mutate(
    station = as.integer(station),
    air_06_18 = rowMeans(
      tmean[, which(colnames(tmean) == "01_2006"):which(colnames(tmean) == "12_2018")]
    ),
  air_95_05 = rowMeans(
      tmean[, which(colnames(tmean) == "01_1995"):which(colnames(tmean) == "12_2005")]
    )
  )

temp_avg_comp <- habitat_press %>%
  dplyr::select(station, temperature_med) %>%
  left_join(air_temp, by = "station") %>%
  rename(water_06_2018 = temperature_med) %>%
  filter(station %in% sem_data$station)

dev.new(width = 6, height = 6, units = "cm")
# i3: mod + shift + space 
png(
  file = mypath("manuscript", "bef_stability", "figs",
    "pairs_temperature_plot.png")
)
pairs(
  temp_avg_comp[, c(2, 4, 5)], pch = 19 
)
dev.off()

mat <- round(cor(temp_avg_comp[, c(2, 4, 5)]), 3)
write.table(mat,
  file = mypath("manuscript", "bef_stability", "result", "cor_mat_temp.txt"),
  sep = ",",
  quote = FALSE,
  row.names = T)
```
